\begin{tightdesc}
\item [Id:] WaveformGenerator
\item [Name:] 
\item [Description:] Complex waveform generator with harmonics, interharmonics, modulation abilities, reference output and reference values for phasor measurement units.
\item [Citation:] First version of the algorithm: U. Pogliano, J.-P. Braun, B. Voljc, and R. Lapuh, ‘Software Platform for PMU Algorithm Testing’, IEEE Transactions on Instrumentation and Measurement, vol. 62, no. 6, pp. 1400–1406, Jun. 2013, doi: 10.1109/TIM.2013.2239051.
\item [Remarks:] If sampling time |Ts| is not supplied, wrapper will calculate |Ts| from sampling frequency |fs| or if not supplied, mean of differences of time series |t| is used to calculate |Ts|. First frequency in |f| is considered as the main signal frequency. Modulation is not yet ready.
\item [License:] MIT License
\item [Provides GUF:] no
\item [Provides MCM:] no
\item [Input Quantities] \rule{0em}{0em}
    \begin{tightdesc}
    \item [Required:] 
        \textsf{Ts} or \textsf{fs} or \textsf{t},\enspace \textsf{L},\enspace \textsf{f},\enspace \textsf{A},\enspace \textsf{ph}
    \item [Optional:] 
        \textsf{l},\enspace \textsf{Fs}
    \item [Descriptions:] \rule{0em}{0em}
        \begin{tightdesc}
            \item[\textsf{A}] -- Amplitude of signal components
            \item[\textsf{Fs}] -- PMU frames per second
            \item[\textsf{L}] -- Number of samples
            \item[\textsf{Ts}] -- Sampling time
            \item[\textsf{f}] -- Frequency of signal components
            \item[\textsf{fs}] -- Sampling frequency
            \item[\textsf{l}] -- Number of samples before t=0
            \item[\textsf{ph}] -- Phase of signal components
            \item[\textsf{t}] -- Time series
        \end{tightdesc}
    \end{tightdesc}
\item [Output Quantities:] \rule{0em}{0em}
    \begin{tightdesc}
        \item[\textsf{t}] -- Time stamps
        \item[\textsf{y}] -- Samples
    \end{tightdesc}
\end{tightdesc}
