\begin{tightdesc}
\item [Id:] OEFPIL
\item [Name:] Optimum Estimate of Function Parameters by Iterated Linearization
\item [Description:] Optimum Estimate of Function Parameters by Iterated Linearization is a software for estimating the parameters of a nonlinear function using iterated linearization via Taylor series. Method is based on Kubáček (2000) ISBN: 80-244-0093-6. The algorithm is a generalization of the procedure given in Köning, R., Wimmer, G. and Witkovský, V. (2014) doi:10.1088/0957-0233/25/11/115001. It was developed at Czech Metrology Institute and Masaryk Univerzity.
\item [Citation:] Kubáček (2000) ISBN: 80-244-0093-6, Köning, R., Wimmer, G. and Witkovský, V. (2014) doi:10.1088/0957-0233/25/11/115001.
\item [Remarks:] For now the implementation knows only linear fit. Full possibility will be implemented later. For now a data to and from OEFPIL are transferred using files. Proper library implementation will be added later.
\item [License:] MIT License
\item [Provides GUF:] yes
\item [Provides MCM:] no
\item [Input Quantities] \rule{0em}{0em}
    \begin{tightdesc}
    \item [Required:] 
        \textsf{x},\enspace \textsf{y},\enspace \textsf{exponents}
    \item [Parameters:] 
        \textsf{exponents}
    \item [Descriptions:] \rule{0em}{0em}
        \begin{tightdesc}
            \item[\textsf{exponents}] -- Exponents of polynomial used to fit, for now only [0 1] possible
            \item[\textsf{x}] -- Independent variable
            \item[\textsf{y}] -- Dependent variable
        \end{tightdesc}
    \end{tightdesc}
\item [Output Quantities:] \rule{0em}{0em}
    \begin{tightdesc}
        \item[\textsf{coefs}] -- Fitted coefficients
        \item[\textsf{exponents}] -- Exponents of polynomial used to fit, for now only [0 1] possible
    \end{tightdesc}
\end{tightdesc}
